---
title: "Import Analysis: Understanding India's Dependence"
author: "Dr Preet Deep Singh"
date: "03/10/2020"
output: 
  word_document: 
    toc: yes
---

## Import Process


For prod in Hs codes 

Summarise by code. 
Filter that code
Plot 5 years trend 

Filter by code, summarise by country exporting and country importing ; get names

## Including Plots

###This is to test whether anything is working

```{r pressure, echo=FALSE}
plot(pressure)
```

# Country Wise
For each country, we are trying to see the top products, the products they are dependent on and the ones we are dependent on them for. 
For example if a country supplies more than 40% of our total requirement for a commodity, we are dependent on them. 
Similarly if one product constitutes more than 20% of a country's total exports to India, then the country is dependent on that product. 
```{r graphs, echo=FALSE, message=FALSE, warning=FALSE}
library(networkD3)
library(dplyr)
library(webshot)
library(htmltools)
library(htmlwidgets)
library(stringr)
library(ggplot2)
remove(list=ls())

CodeCountry <- read.csv("CodeCountry.csv")
CodeCountry$HSCode<-ifelse(nchar(CodeCountry$HSCode)==7, paste0(0,CodeCountry$HSCode),CodeCountry$HSCode)#Convert all to 8
CodeCountry$Y1920P<-as.numeric((CodeCountry$Y1920P))
#sum(CodeCountry$Y1920P,na.rm=TRUE) #Check335566365osmthing
#Get 2,4,6 digits from the second column and summarise it later.
CodeCountry$rupeeamount<-CodeCountry$Y1920P #On 23Jul Dollar conversion
CodeCountry$dollaramount<-CodeCountry$Y1920P*100000/74000000 #divide by 74 000 000, multiply by 100000
CodeCountry$Y1920P<-CodeCountry$dollaramount#So that you dont have to change the rest of the code
CodeCountry<-  select(CodeCountry,Country,HSCode,Y1920P)

CommodityOrg <- read.csv("20200715AllImpDWworking.csv")
CommodityOrg$HSCode<-ifelse(nchar(CommodityOrg$HSCode)==7, paste0(0,CommodityOrg$HSCode),CommodityOrg$HSCode)#Convert all to 8
  
## We need to Get top ten 2 digit(sector) for each country

  CodeCountry$hsc2d<-substr(CodeCountry$HSCode, 1, 2) #Get 2 digits
  Summary2Dig <- summarize(group_by(CodeCountry, hsc2d,Country), total = sum(Y1920P, na.rm = TRUE))
  hsnChapter <- read.csv("hsnChapter.csv") #This is to get the names of the Two digit things
  hsnChapter$HS.Code<-ifelse(nchar(hsnChapter$HS.Code)==1, paste0(0,hsnChapter$HS.Code),hsnChapter$HS.Code)
  
  Summary2DigNames<-merge(Summary2Dig,hsnChapter, by.x="hsc2d", by.y="HS.Code",all.x=TRUE,all.y=FALSE)
  Summary2DigNames$hsc2d<-paste(Summary2DigNames$hsc2d,Summary2DigNames$CodeConvert)
  Summary2DigNames<-select(Summary2DigNames,Country,hsc2d,total)

  
  CodeWise<-summarize(group_by(CodeCountry, HSCode), sum1920=sum(Y1920P, na.rm = TRUE))
CodeCountry<-merge(CodeCountry,CodeWise, by = "HSCode",all.x=TRUE, all.y=FALSE)
CodeCountry<-mutate(CodeCountry,oftotalprod=Y1920P/sum1920) #In order to get percentage of total

CommodityOrg<-select(CommodityOrg, "HSCode","Commodity")
CodeCountry<-merge(CodeCountry,CommodityOrg, by = "HSCode")
CodeCountry<-CodeCountry[order(CodeCountry$Country),]
  "TEsting a Heading"
  for (i in 1:length(unique(CodeCountry$Country))){
    country<-unique(CodeCountry$Country)[i]
    Summary2DigNames2<-filter(Summary2DigNames,Summary2DigNames$Country==country)
    links2<-Summary2DigNames2
    links<-links2[order(-links2$total),]
    
    if (nrow(links) > 6) {
      links <- links[1:6, ]
      diffrows<-(nrow(links2)-nrow(links))
      diffvalue<-sum(links2$total)-sum(links$total)
      links<-as.data.frame(links)
      links<-rbind(links, list(country, "OtherProducts", diffvalue))
  #    links<-rbind(links, list(country, paste("Other",diffrows,"products worth USD",prettyNum(diffvalue,big.mark=",", preserve.width="none"),"million" ), diffvalue)) #This has the number also
    }

library(ggplot2)
links<-links[order(-links$total),]
a<-ggplot(links,aes(x=reorder(hsc2d,-total),total)) + geom_bar(stat="identity") + scale_x_discrete(guide = guide_axis(n.dodge=3)) +xlab("Top Chapters")+ylab("Amount in USD million")+ ggtitle(paste("Top import chapters from",country))+ labs(caption=paste("This graph shows the chapter number and description of the chapters that have the highest import value from ",country," for the year 2019-2020.")) + theme(
  plot.caption = element_text(hjust = 0))+ 
    theme(plot.title = element_text(size = 8, face = "bold"))


cat(paste("#HEADING \nThis is ",country,". \nTotal imports in 2019-20 were USD",prettyNum(sum(links$total, na.rm = TRUE),big.mark=",", preserve.width="none"),"million."))

links3<-mutate(links2, sum=sum(links$total, na.rm = TRUE))
links3<-mutate(links3, oftotalcountry= total/sum)
links3<-filter(links3, oftotalcountry>0.25)
ifelse(length(links3$hsc2d)==1,
print(paste(country,"is dependent on",length(links3$hsc2d),"product for its exports to India.", "Chapter", links[1,2],"makes up approximately", round((links[1,3])/sum(links$total)*100), "percent of the total imports from",country,"." )),
print("The country is not dependent on any one product for exports to India"))



CodeCountry1<-filter(CodeCountry,Country==country)
CodeCountry1<-filter(CodeCountry1,oftotalprod>0.40)

print(paste("There are ",length(CodeCountry1[,2]),"products for which we import more than 40% of our total requirement from ",country,". These are"))
#print(unique(CodeCountry1$Commodity))
print(paste0(unlist(CodeCountry1$Commodity), collapse =" ",","))# This allows it to be in one line

print(paste("The top chapters under which goods are imported from",country, "are displayed in graph below."))
print(a)

}
